Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Recap functor categories [X, C] where X a set.

>>>>

\begin{definition}[Reindexing]
For any function $f: X \to Y$ define the \emph{reindexing} functor $\reindex{-}{f}: \Func{Y}{\cat{C}} \to
\Func(X,\cat{C})$ which:
\begin{itemize}
\item sends any $J$-indexed family $X$ to the $I$-indexed family $\reindex{X}{f}$ where $\reindex{X}{f}_i =
X_{f(i)}$ for any $i \in I$;
\item sends any morphism $g: X \to Y$ between $J$-indexed families to the morphism $\reindex{g}{f}:
\reindex{X}{f} \to \reindex{Y}{f}$ where $\reindex{g}{f}_i = g_{f(i)}$.
\end{itemize}
\end{definition}
